---
title: "data_exclusion"
author: "Paula Adamopoulos, Christopher Huebel, Helena Davies"
date: "15/03/2025"
output:
  html_document:
    toc: true
    toc_depth: 4
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    df_print: paged
editor_options: 
  markdown: 
    wrap: 72
---

# Setup

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)
```

## Clear workspace

```{r Clear worksapce}
rm(list = ls())
```


Read in file with path to ilovedata channel on Teams
Ensure that your credentials directory is correctly located
```{r Read in paths file}
source(file = "credentials/paths.R")
```


Add the add_numeric function - used to convert character variables into numeric variables.
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = paste0(ilovedata_scripts, "functions/add_numeric.R"))
source(file = paste0(ilovedata_scripts, "functions/remove_duplicates.R"))
source(file = paste0(ilovedata_scripts, "functions/sumscores.R"))
source(file = paste0(ilovedata_scripts, "functions/package_check.R"))
source(file = paste0(ilovedata_scripts, "functions/imp_check.R"))
source(file = paste0(ilovedata_scripts, "functions/recode_check.R"))
```


## Install packages

```{r Install packages}
#install.packages("ggformula")
#install.packages("tidyverse")
```

## Load packages

```{r Load packages}
library(openxlsx)
library(gtsummary)
library(ggconsort)
library(tidyverse)
```

## Retrieve the recent date

```{r Recent date}
date = Sys.Date()
date
```

## Read in data

```{r Read in data}
dat <- read_rds(
  file = paste0(filepath_cleaned_data,"dat_variable_creation", date, ".rds"))
```


Psychiatric diagnoses
```{r Psychiatric diagnoses vector}
psy_dx_factors <- c(
  "mhd.mdd",
  "mhd.gad",
  "mhd.social_anxiety",
  "mhd.specific_phobia",
  "mhd.agoraphobia",
  "mhd.panic_disorder",
  "mhd.panic_attacks",
  "mhd.bipolar_disorder",
  "mhd.ocd",
  "mhd.bdd",
  "mhd.an",
  "mhd.atypical_an",
  "mhd.bn",
  "mhd.bed"
)
```

Analysis variables vector

```{r}
analysis_variables_vector <- c(
  "phq9.sum_score", 
  "phq.Q9_suicidality_binary_numeric", # Suicidality
  "phq.Q9_suicidality_binary",
  "gender",
  "sex",
  "age",
  "bmi",
  "height_m",
  "ethnicity",
  "sexual_orientation",
  "dem.highest_education_collapsed",
  psy_dx_factors
)
```


# Exclusion criteria

## Exclusion table

-555 'Not applicable' response from participant
-666 Implausible response/value
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say

```{r Exclusion table demographics exposure outcome}
dat %>%
  select(
    age,
    gender,
    sex,
    ethnicity,
    sexual_orientation,
    height_m,
    bmi,
    dem.highest_education_collapsed,
    phq9.sum_score,
  "mhd.mdd",
  "mhd.gad",
  "mhd.social_anxiety",
  "mhd.specific_phobia",
  "mhd.agoraphobia",
  "mhd.panic_disorder",
  "mhd.panic_attacks",
  "mhd.bipolar_disorder",
  "mhd.ocd",
  "mhd.bdd",
  "mhd.an",
  "mhd.atypical_an",
  "mhd.bn",
  "mhd.bed"
) %>%
  gtsummary::tbl_summary()
```


# Study cohorts


```{r}
study_cohorts <- 
  dat %>%
  cohort_start("Consented") %>%
  # Define cohorts using named expressions --------------------
  # Notice that you can use previously defined cohorts in subsequent steps
  cohort_define(
    consented = .full,
    
    nogender = .full %>%
      drop_na(gender),
    
    missing_gender = anti_join(
      x = .full,
      y =  nogender,
      by = "ID"),
    
    nogender.nosex = nogender %>%
      drop_na(sex),
    
     missing_sex = anti_join(
      x = nogender,
      y =  nogender.nosex,
      by = "ID"),
    
    
    nogender.nosex.nomhd = 
      nogender.nosex %>%
      filter(
      !if_all(all_of(psy_dx_factors), is.na)
        ),
    
    missing_mhd = anti_join(
      nogender.nosex,
      nogender.nosex.nomhd,
      by = "ID")
    
  ) %>%
  # Provide text labels for subsamples ---------------------------
  cohort_label(
    consented =
      "Consented",
    nogender =
      "With gender",
    nogender.nosex =
      "With gender, sex",
    nogender.nosex.nomhd =
      "With gender, sex, MHD",
    
    missing_gender = "Excluded: No gender",
    missing_sex = "Ecluded: No sex",
    missing_mhd = "Excluded No mental health diagnosis"
  )
```

# Consort diagram (flow chart)

```{r CONSORT diagram}
study_consort <- study_cohorts %>%
  consort_box_add(
    name = "consented",
    x = 0,
    y = -10,
    label =  cohort_count_adorn(
      study_cohorts,
      .full)
  ) %>%
  consort_box_add(
    "missing_gender",
    x = 5,
    y = -15,
    label =  cohort_count_adorn(study_cohorts, missing_gender)
  ) %>%
  consort_box_add(
    name = "nogender",
    x = 0,
    y = -20,
    label =  cohort_count_adorn(
      study_cohorts,
      nogender)
  ) %>%
  consort_box_add(
    "missing_sex",
    x = 5,
    y = -25,
    label =  cohort_count_adorn(study_cohorts, missing_sex)
  ) %>%
  consort_box_add(
    name = "nogender.nosex",
    x = 0,
    y = -30,
    label =  cohort_count_adorn(
      study_cohorts,
      nogender.nosex)
    ) %>%
  consort_box_add(
    "missing_mhd",
    x = 5,
    y = -35,
    label =  cohort_count_adorn(study_cohorts, missing_mhd)
  ) %>%
  consort_box_add(
    name = "nogender.nosex.nomhd",
    x = 0,
    y = -40,
    label =  cohort_count_adorn(
      study_cohorts,
      nogender.nosex.nomhd)
  ) %>%
  consort_arrow_add(
    end = "nogender", end_side = "top", start_x = 0, start_y = -10
  ) %>%
  consort_arrow_add(
    end = "missing_gender", end_side = "left", start_x = 0, start_y = -15
  ) %>%
  consort_arrow_add(
    end = "nogender.nosex", end_side = "top", start_x = 0, start_y = -20
  ) %>%
  consort_arrow_add(
    end = "missing_sex", end_side = "left", start_x = 0, start_y = -25
  ) %>%
  consort_arrow_add(
    end = "nogender.nosex.nomhd", end_side = "top", start_x = 0, start_y = -30
  ) %>%
  consort_arrow_add(
    end = "missing_mhd", end_side = "left", start_x = 0, start_y = -35
  )
```

## Figure

```{r fig.height=8, fig.width=12}
study_consort %>%
  ggplot() + 
  geom_consort() +
  theme_consort(margin_h = 25, margin_v = 1)
```

## Save figure

+++ That's currently not working. I have opened an issue on the GitHub
https://github.com/tgerke/ggconsort/issues/26

```{r eval=FALSE, include=FALSE}
ggsave(
  filename = paste0("flow_chart_n_", date, ".pdf"),
  plot = study_consort,
  device = "pdf",
  path = filepath_plots,
  scale = 1,
  width = 12,
  height = 8,
  units = "in",
  dpi = 300
)
```

# Attrition variable

```{r}
names(study_cohorts$data)
```

## IDs after exclusion
```{r IDs present after exclusion}
IDs_present <-
  as.vector(
  study_cohorts$data$nogender.nomhd$ID
  )
```


```{r}
dat_consented <- study_cohorts$data$consented
```


```{r attrition variable}
dat_consented <- dat_consented %>%
  mutate(
    present =
      if_else(
        condition = ID %in% IDs_present,
        true = "Present",
        false = "Excluded",
        missing = NA_character_
      ) 
  )
```


# Exclusion manually

## gender

```{r Exclusion gender}
dim(dat)

nogender <- dat %>%
  drop_na(gender)

missing_gender <- abs(nrow(nogender)-nrow(dat))
missing_gender
```

`r abs(missing_gender)` participants excluded due to missing gender.

## sex

```{r Exclusion age}
dim(nogender)

nogender.nosex <- nogender %>%
  drop_na(sex)

missing_sex <- nrow(nogender.nosex)-nrow(nogender)
missing_sex
```

## mhd


```{r Exclusion mhd}
dim(nogender.nosex)

nogender.nosex.nomhd <- nogender.nosex %>%
  filter(
    if_all(all_of(psy_dx_factors), is.na)
  )

missing_mhd <- 
  nrow(nogender.nosex) - 
  nrow(nogender.nosex.nomhd)
missing_mhd
```

`r abs(missing_mhd)` participants excluded due to missing mhd.

```{r Final}
nrow(nogender.nosex.nomhd)
nrow(nogender.nosex)

nrow(nogender.nosex[nogender.nosex$gender == "Trans woman", ])-nrow(nogender.nosex.nomhd[nogender.nosex.nomhd$gender == "Trans woman", ])
```

## Final

Final *n* = `r abs(nrow(nogender.noage.noethnicity.nosexuality.nobmiheight.noedu.nomhd))`

Copy tibble after exclusion

```{r Move data frame}
dat_after_exclusion <- 
  nogender.nosex.nomhd
nrow(dat_after_exclusion)
```

# Write rds file

```{r write rds file exclusion}
dat_after_exclusion %>%
  write_rds(
  file =  paste0(filepath_cleaned_data,"dat_after_exclusion", date, ".rds")
  )
```

dat_consented

```{r write rds file attrition}
dat_consented %>%
  write_rds(
  file =  paste0(filepath_cleaned_data,"dat_consented_attrition", date, ".rds")
  )
```
