---
title: "data_exclusion"
author: ""
date: ""
output:
  html_document:
    toc: true
    toc_depth: 4
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    df_print: paged
editor_options: 
  markdown: 
    wrap: 72
---

# Setup

```{r Setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      comment=NA,
                      prompt=FALSE,
                      cache=FALSE)
```

## Clear workspace

```{r Clear worksapce}
rm(list = ls())
```


Read in file with path to ilovedata channel on Teams
```{r Read in paths file}
source(file = "credentials/paths.R")
```


Add the add_numeric function - used to convert character variables into numeric variables.
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = paste0(ilovedata_scripts, "functions/add_numeric.R"))
source(file = paste0(ilovedata_scripts, "functions/remove_duplicates.R"))
source(file = paste0(ilovedata_scripts, "functions/sumscores.R"))
source(file = paste0(ilovedata_scripts, "functions/package_check.R"))
source(file = paste0(ilovedata_scripts, "functions/imp_check.R"))
source(file = paste0(ilovedata_scripts, "functions/recode_check.R"))
```


## Install packages

```{r Install packages}
#install.packages("ggformula")
#install.packages("tidyverse")
```

## Load packages

```{r Load packages}
library(gtsummary)
library(DiagrammeR)
library(DiagrammeRsvg)
library(rsvg)
library(tidyverse)
```

## Retrieve the recent date

```{r Recent date}
date = Sys.Date()
```

## Read in data

```{r Read in data}
dat <- read_rds(
  file = paste0(filepath_cleaned_data_coping_nbr,"dat_variable_creation_coping_nbr", date, ".rds"))
```

```{r view}
dat %>% 
  names
```

# Psychiatric diagnoses vector
```{r Psychiatric diagnoses vector}
psy_dx_numeric <- c(
  "mhd.mdd_cop_numeric",
  "mhd.gad_cop_numeric",
  "mhd.social_anxiety_cop_numeric",
  "mhd.specific_phobia_cop_numeric",
  "mhd.agoraphobia_cop_numeric",
  "mhd.panic_disorder_cop_numeric",
  "mhd.panic_attacks_cop_numeric",
  "mhd.bipolar_disorder_cop_numeric",
  "mhd.ocd_cop_numeric",
  "mhd.bdd_cop_numeric",
  "mhd.an_cop_numeric",
  "mhd.atypical_an_cop_numeric",
  "mhd.bn_cop_numeric",
  "mhd.atypical_bn_cop_numeric",
  "mhd.bed_cop_numeric",     
  "mhd.schizophrenia_cop_numeric",
  "mhd.ptsd_cop_numeric",
  "mhd.addadhd_cop_numeric"
)
```

# Analysis variables vector

```{r Analysis variables vector}
analysis_variables_vector <- c(
  "phq9.sum_score", 
  "phq.Q9_suicidality_binary_numeric", # Suicidality
  "phq.Q9_suicidality_binary",
  "gender",
  "sex",
  "age",
  "bmi",
  "height_m",
  "ethnicity",
  "sexual_orientation",
  "dem.highest_education_collapsed",
  psy_dx_numeric
)
```


# Exclusion criteria

-555 'Not applicable' response from participant
-666 Implausible response/value
-777 Seen but not answered
-888 Don't know
-999 Prefer not to answer/Prefer not to say

```{r table before exclusion}
dat %>%
  select(
    age,
    gender,
    sex,
    ethnicity,
    #sexual_orientation,
    height_m,
    bmi,
    employ.highest_education_collapsed_cop,
  "mhd.mdd_cop_numeric",
  "mhd.gad_cop_numeric",
  "mhd.social_anxiety_cop_numeric",
  "mhd.specific_phobia_cop_numeric",
  "mhd.agoraphobia_cop_numeric",
  "mhd.panic_disorder_cop_numeric",
  "mhd.panic_attacks_cop_numeric",
  "mhd.bipolar_disorder_cop_numeric",
  "mhd.ocd_cop_numeric",
  "mhd.bdd_cop_numeric",
  "mhd.an_cop_numeric",
  "mhd.atypical_an_cop_numeric",
  "mhd.bn_cop_numeric",
  "mhd.atypical_bn_cop_numeric",
  "mhd.bed_cop_numeric",     
  "mhd.schizophrenia_cop_numeric",
  "mhd.ptsd_cop_numeric",
  "mhd.addadhd_cop_numeric"
) %>%
  gtsummary::tbl_summary()
```


# Exclusion manually

## gender

```{r Exclusion gender}
dim(dat)

nogender <- dat %>%
  drop_na(gender)

missing_gender <- abs(nrow(nogender)-nrow(dat))
missing_gender
```

## Final

Final *n* = `r abs(nrow(nogender.nodisorder))`for gender

```{r name}
dat_after_exclusion_gender <- 
  nogender
nrow(dat_after_exclusion_gender)
```

# Write rds file

```{r write rds file exclusion}
dat_after_exclusion_gender %>%
  write_rds(
  file =  paste0(filepath_cleaned_data_coping_nbr,"dat_after_exclusion_gender_coping_nbr", date, ".rds")
  )
```

