---
title: "Descriptives table"
author: ''
date: ''
output:
  html_document:
    toc: true
    toc_depth: 4
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    df_print: paged
  pdf_document:
    toc: true
    toc_depth: '4'
editor_options:
  markdown:
    wrap: 72
---

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r clear global environment}
rm(list = ls(all.names = TRUE)) 
```

```{r Read in paths file}
source(file = "credentials/paths.R")
```

Add the add_numeric function - used to convert character variables into numeric variables.
Add the sumscores function - used to generate sumscores
Add the package_check function - used to install and load dependencies
```{r Read in functions}
source(file = paste0(ilovedata_scripts, "functions/add_numeric.R"))
source(file = paste0(ilovedata_scripts, "functions/remove_duplicates.R"))
source(file = paste0(ilovedata_scripts, "functions/sumscores.R"))
source(file = paste0(ilovedata_scripts, "functions/package_check.R"))
source(file = paste0(ilovedata_scripts, "functions/imp_check.R"))
source(file = paste0(ilovedata_scripts, "functions/recode_check.R"))
```

```{r Load packages}
library(flextable)
library(officer)
library(dplyr)
library(gtsummary)
library(gt)
library(summarytools)
library(tidyverse)
```

```{r set current date}
date <- Sys.Date()
#date <- "2026-03-22"
date
```

```{r Load data gender_cop_nbr}
dat_gender <- read_rds(
  file =
    paste0(filepath_cleaned_data_coping_nbr,"dat_after_exclusion_gender_coping_nbr", date, ".rds")
)
nrow(dat_gender)
```

```{r sort}
# sort just individuals from coping_nbr with genetic info
dat_prs_depression <- read.table(filepath_prs_depression_no_mhd, header = TRUE, sep = "\t", stringsAsFactors = FALSE)
#in the other prs gropus are the same number of people
dat_gender <- merge(dat_prs_depression, dat_gender, by.x = "FID", by.y = "ID")

nrow(dat_gender)
```

```{r Load data gender_glad}
dat_gender_glad <- read_rds(
  file =
    paste0(filepath_cleaned_data,"dat_after_exclusion_gender", date, ".rds")
)
```

```{r Gender  create category trans person}
#if not enough trans women

#dat <- dat %>%
 # mutate(gender = case_when(
  #  gender == "Trans man" ~ "Trans person",
   # gender == "Trans woman" ~ "Trans person",
    #TRUE ~ gender
  #))
```

```{r Gender check}
dat_gender %>%
  freq(gender)
```


```{r numeric}
dx_labels <- c(
  mhd.mdd_cop                = "MDD",
  mhd.gad_cop                = "GAD",
  mhd.social_anxiety_cop     = "Social anxiety",
  mhd.specific_phobia_cop   = "Specific phobia",
  mhd.agoraphobia_cop        = "Agoraphobia",
  mhd.panic_attacks_cop      = "Panic attacks",
  mhd.bipolar_disorder_cop   = "Bipolar disorder",
  mhd.ocd_cop                = "OCD",
  mhd.bdd_cop                = "BDD",
  mhd.an_cop                 = "AN",
  mhd.atypical_an_cop        = "Atypical AN",
  mhd.bn_cop                 = "BN",
  mhd.bed_cop                = "BED",
  mhd.schizophrenia_cop      = "Schizophrenia",
  mhd.ptsd_cop               = "PTSD",
  mhd.addadhd_cop            = "ADD/ADHD"
  
)

for (v in names(dx_labels)) {

  numeric_name <- paste0(v, "_numeric")

  dat_gender[[v]] <- factor(
    dat_gender[[numeric_name]],
    levels = c(0, 1),
    labels = c(
      paste("Not", dx_labels[[v]]),
      dx_labels[[v]]
    )
  )
}

#dat_gender$mhd.mdd_cop
```

# tables
## gender demographics coping_nbr

```{r dat_gender_demographics}
dat_gender_demographics <- dat_gender %>%
  select(
    age,
    sex,
    gender,
    ethnicity,
    #sexual_orientation,
    height_m,
    bmi,
    employ.highest_education_collapsed_cop,
    #phq9.sum_score,
    #gad7.sum_score,
    mhd.mdd_cop,
  mhd.gad_cop,
  mhd.social_anxiety_cop,
  mhd.specific_phobia_cop,
  mhd.agoraphobia_cop,
  #mhd.panic_disorder_cop,
  mhd.panic_attacks_cop,
  mhd.bipolar_disorder_cop,
  mhd.ocd_cop,
  mhd.bdd_cop,
  mhd.an_cop,
  #mhd.atypical_an_cop,
  mhd.bn_cop,
  #mhd.atypical_bn_cop,
  mhd.bed_cop,
  mhd.schizophrenia_cop,
  mhd.ptsd_cop,
  mhd.addadhd_cop,
  )
```

```{r variable names}
names(dat_gender_demographics)
```

```{r combine trans person and selfdefine 1}
unique(dat_gender_demographics$gender)
dat_gender_demographics <- dat_gender_demographics %>%
  mutate(gender = case_when(
    gender %in% c("Trans woman", "Trans man", "Self-define") ~ "Trans person or self-define",
    TRUE ~ gender 
  ))
table(dat_gender_demographics$gender)
```

```{r gender sample}
summary_table_gender_sample <-
  dat_gender_demographics %>%
  gtsummary::tbl_summary(
    label = list(
      gender = "Gender",
      sex = "Biological sex",
      age = "Age [years]",
      ethnicity = "Ethnicity",
      sexual_orientation = "Sexual orientation",
      height_m = "Height [m]",
      bmi = "BMI [kg/m2]",
      employ.highest_education_collapsed_cop = "Highest education",
      phq9.sum_score = "PHQ9 score",
      gad7.sum_score = "GAD7 score",
      phq.Q9_suicidality_binary = "Suicidality",
      mhd.mdd_cop = "Major depressive disorder",
      mhd.gad_cop = "Generalised anxiety disorder",
      mhd.social_anxiety_cop = "Social anxiety",
      mhd.specific_phobia_cop = "Specific phobia",
      mhd.agoraphobia_cop = "Agoraphobia",
      #mhd.panic_disorder = "Panic disorder",
      mhd.panic_attacks_cop = "Panic attacks",
      mhd.bipolar_disorder_cop ="Bipolar disorder",
      mhd.ocd_cop = "Obsessive-compulsive disorder",
      mhd.bdd_cop = "Body dysmorphic disorder",
      mhd.an_cop = "Anorexia nervosa", 
      #mhd.atypical_an_cop = "Atypical anorexia nervosa",
      mhd.bn_cop = "Bulimia nervosa",
      mhd.bed_cop = "Binge-eating disorder",
      mhd.schizophrenia_cop = "Schizophrenia",
      mhd.ptsd_cop = "PTSD",
      mhd.addadhd_cop = "ADD or ADHD"
      ),
    type = list(
      gender = "categorical",
      dem.sex = "categorical",
      age = "continuous2",
      ethnicity = "categorical",
      sexual_orientation = "categorical",
      height_m = "continuous2",
      bmi = "continuous2",
      employ.highest_education_collapsed_cop = "categorical",
      phq9.sum_score = "continuous2",
      gad7.sum_score = "continuous2",
      phq.Q9_suicidality_binary = "dichotomous",
      mhd.mdd_cop = "dichotomous",
      mhd.gad_cop = "dichotomous",
      mhd.social_anxiety_cop = "dichotomous",
      mhd.specific_phobia_cop = "dichotomous",
      mhd.agoraphobia_cop = "dichotomous",
      #mhd.panic_disorder = "dichotomous",
      mhd.panic_attacks_cop = "dichotomous",
      mhd.bipolar_disorder_cop = "dichotomous",
      mhd.ocd_cop = "dichotomous",
      mhd.bdd_cop = "dichotomous",
      mhd.an_cop = "dichotomous",
     # mhd.atypical_an_cop = "dichotomous",
      mhd.bn_cop = "dichotomous",
      mhd.bed_cop = "dichotomous",
      mhd.schizophrenia_cop = "dichotomous",
      mhd.ptsd_cop = "dichotomous",
      mhd.addadhd_cop = "dichotomous"
      ),
    value = list(
      phq.Q9_suicidality_binary = "Any suicidality",
      mhd.mdd_cop = "MDD",
      mhd.gad_cop = "GAD",
      mhd.social_anxiety_cop = "Social anxiety",
      mhd.specific_phobia_cop = "Specific phobia",
      mhd.agoraphobia_cop = "Agoraphobia",
      #mhd.panic_disorder = "Panic disorder",
      mhd.panic_attacks_cop = "Panic attacks",
      mhd.bipolar_disorder_cop = "Bipolar disorder",
      mhd.ocd_cop = "OCD",
      mhd.bdd_cop = "BDD",
      mhd.an_cop = "AN", 
      #mhd.atypical_an_cop = "Atypical AN",
      mhd.bn_cop = "BN",
      mhd.bed_cop = "BED",
      mhd.schizophrenia_cop = "Schizophrenia",
      mhd.ptsd_cop = "PTSD",
      mhd.addadhd_cop = "ADD/ADHD"
      ),
    missing_text = "Not answered",
    digits = list(
      all_categorical() ~ c(0, 1),
      all_dichotomous() ~ c(0, 1)),
    
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})",  "{min} - {max}")
      )
    ) %>%
  bold_labels()


summary_table_gender_sample
```

## gender demographics glad

```{r dat_gender_demographics_glad}
dat_gender_demographics_glad <- dat_gender_glad %>%
  select(
    age,
    sex,
    gender,
    ethnicity,
    sexual_orientation,
    height_m,
    bmi,
    dem.highest_education_collapsed,
    #phq9.sum_score,
    #gad7.sum_score,
    any_mdd_diagnosis,
    any_gad_diagnosis,
    phq.Q9_suicidality_binary,
    mhd.mdd,
    mhd.gad,
    mhd.social_anxiety,
    mhd.specific_phobia,
    mhd.agoraphobia,
    #mhd.panic_disorder,
    mhd.panic_attacks,
    mhd.bipolar_disorder,
    mhd.ocd,
    mhd.bdd,
    mhd.an,
    mhd.atypical_an,
    mhd.bn,
    mhd.bed,
    mhd.schizophrenia,
    mhd.ptsd,
    mhd.addadhd,
  )
```

```{r combine trans person and selfdefine}
unique(dat_gender_demographics_glad$gender)
dat_gender_demographics_glad <- dat_gender_demographics_glad %>%
  mutate(gender = case_when(
    gender %in% c("Trans woman", "Trans man", "Self-define") ~ "Trans person or self-define",
    TRUE ~ gender  # Behält alle anderen (cis man, cis women, etc.) so bei, wie sie sind
  ))
table(dat_gender_demographics_glad$gender)
```

```{r gender sample 1}
summary_table_gender_sample_glad <-
  dat_gender_demographics_glad %>%
  gtsummary::tbl_summary(
    label = list(
      gender = "Gender",
      sex = "Biological sex",
      age = "Age [years]",
      ethnicity = "Ethnicity",
      sexual_orientation = "Sexual orientation",
      height_m = "Height [m]",
      bmi = "BMI [kg/m2]",
      dem.highest_education_collapsed = "Highest education",
      phq9.sum_score = "PHQ9 score",
      gad7.sum_score = "GAD7 score",
      phq.Q9_suicidality_binary = "Suicidality",
      #mhd.mdd = "Major depressive disorder",
      #mhd.gad = "Generalised anxiety disorder",
      any_mdd_diagnosis = "Major depressive disorder",
      any_gad_diagnosis = "Generalised anxiety disorder",
      mhd.social_anxiety = "Social anxiety",
      mhd.specific_phobia = "Specific phobia",
      mhd.agoraphobia = "Agoraphobia",
      #mhd.panic_disorder = "Panic disorder",
      mhd.panic_attacks = "Panic attacks",
      mhd.bipolar_disorder ="Bipolar disorder",
      mhd.ocd = "Obsessive-compulsive disorder",
      mhd.bdd = "Body dysmorphic disorder",
      mhd.an = "Anorexia nervosa", 
      mhd.atypical_an = "Atypical anorexia nervosa",
      mhd.bn = "Bulimia nervosa",
      mhd.bed = "Binge-eating disorder",
      mhd.schizophrenia = "Schizophrenia",
      mhd.ptsd = "PTSD",  
      mhd.addadhd = "ADD or ADHD"
      ),
    type = list(
      gender = "categorical",
      dem.sex = "categorical",
      age = "continuous2",
      ethnicity = "categorical",
      sexual_orientation = "categorical",
      height_m = "continuous2",
      bmi = "continuous2",
      dem.highest_education_collapsed = "categorical",
      phq9.sum_score = "continuous2",
      gad7.sum_score = "continuous2",
      phq.Q9_suicidality_binary = "dichotomous",
      #mhd.mdd = "dichotomous",
      #mhd.gad = "dichotomous",
      any_mdd_diagnosis = "dichotomous",
      any_gad_diagnosis = "dichotomous",
      mhd.social_anxiety = "dichotomous",
      mhd.specific_phobia = "dichotomous",
      mhd.agoraphobia = "dichotomous",
      #mhd.panic_disorder = "dichotomous",
      mhd.panic_attacks = "dichotomous",
      mhd.bipolar_disorder = "dichotomous",
      mhd.ocd = "dichotomous",
      mhd.bdd = "dichotomous",
      mhd.an = "dichotomous",
      mhd.atypical_an = "dichotomous",
      mhd.bn = "dichotomous",
      mhd.bed = "dichotomous",
      mhd.schizophrenia = "dichotomous",
      mhd.ptsd = "dichotomous",
      mhd.addadhd = "dichotomous"
      
      ),
    value = list(
      phq.Q9_suicidality_binary = "Any suicidality",
      #mhd.mdd = "MDD",
      #mhd.gad = "GAD",
      any_mdd_diagnosis = "MDD",
      any_gad_diagnosis = "GAD",
      mhd.social_anxiety = "Social anxiety",
      mhd.specific_phobia = "Specific phobia",
      mhd.agoraphobia = "Agoraphobia",
      #mhd.panic_disorder = "Panic disorder",
      mhd.panic_attacks = "Panic attacks",
      mhd.bipolar_disorder = "Bipolar disorder",
      mhd.ocd = "OCD",
      mhd.bdd = "BDD",
      mhd.an = "AN", 
      mhd.atypical_an = "Atypical AN",
      mhd.bn = "BN",
      mhd.bed = "BED",
      mhd.schizophrenia = "Schizophrenia",
      mhd.ptsd = "PTSD",
      mhd.addadhd = "ADD/ADHD"
      ),
    missing_text = "Not answered",
    digits = list(
      all_categorical() ~ c(0, 1),
      all_dichotomous() ~ c(0, 1)),
    
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})",  "{min} - {max}")
      )
    ) %>%
  bold_labels()

summary_table_gender_sample_glad
```

## coping_nbr + glad

```{r nebeneinander}
tbl_gender_sample <-
  summary_table_gender_sample %>%
  gtsummary::modify_table_body(
    ~ .x %>% dplyr::mutate(variable = label)
  )

tbl_gender_glad <-
  summary_table_gender_sample_glad %>%
  gtsummary::modify_table_body(
    ~ .x %>% dplyr::mutate(variable = label)
  )
tbl_combined <-
  gtsummary::tbl_merge(
    tbls = list(tbl_gender_sample, tbl_gender_glad),
    tab_spanner = c("Coping_nbr", "GLAD")
  )
tbl_combined
```

### Save as a word document

```{r word properties 1}
sect_properties1 <- officer::prop_section(
  page_size = page_size(
    orient = "portrait",
    width = 8.3,
    height = 11.7
  ),
  type = "continuous",
  page_margins = page_mar()
)
```

```{r summary_table_whole_sample as word document}
tbl_combined %>%
  as_flex_table() %>%
  flextable::save_as_docx(
    path = paste0(LGBTQ_folder, "tables/", date, "/LGBTQ_descriptives_glad_coping_nbr", date, ".docx"),
    pr_section = sect_properties1
  )
```

## Desciptive tables for gender coping_nbr

```{r descriptives for gender coping _nbr}
dat_gender_demographics <-
  dat_gender_demographics %>%
  select(-age, -height_m, -bmi)

```

```{r summary_table_clinical_gender 1}
summary_table_clinical_gender <-
  dat_gender_demographics %>%
  gtsummary::tbl_summary(
    by = gender, 
    missing = "no",
    label = list(
      sex = "Biological sex",
      sexual_orientation = "Sexual orientation",
      ethnicity = "Ethnicity",
      employ.highest_education_collapsed_cop = "Highest education",
      mhd.mdd_cop = "Major depressive disorder",
      mhd.gad_cop = "Generalised anxiety disorder",
      #any_mdd_diagnosis = "Major depressive disorder",
      #any_gad_diagnosis = "Generalised anxiety disorder",
      mhd.social_anxiety_cop = "Social Anxiety",
      mhd.specific_phobia_cop = "Specific phobia",
      mhd.agoraphobia_cop = "Agoraphobia",
      mhd.panic_disorder_cop = "Panic disorder",
      mhd.panic_attacks_cop = "Panic attacks",
      mhd.bipolar_disorder_cop ="Bipolar disorder",
      mhd.ocd_cop = "Obsessive-compulsive disorder",
      mhd.bdd_cop = "Body dysmorphic disorder",
      mhd.an_cop = "Anorexia nervosa", 
      mhd.atypical_an_cop = "Atypical anorexia nervosa",
      mhd.bn_cop = "Bulimia nervosa",
      mhd.bed_cop = "Binge-eating disorder",
      mhd.schizophrenia_cop = "Schizophrenia",
      mhd.ptsd_cop = "PTSD",
      mhd.addadhd_cop = "ADD or ADHD",
      
      phq.Q9_suicidality_binary_cop = "Suicidality"
    ),
     
    type = list(
      sex = "categorical",
      gender = "categorical",
      sexual_orientation = "categorical",
      
      employ.highest_education_collapsed_cop = "categorical",
      #phq9.sum_score = "continuous2",
      #gad7.sum_score = "continuous2",
      #cidid.mdd_diagnosis = "dichotomous",
      #cidia.diagnosis = "dichotomous",
      mhd.mdd_cop = "dichotomous",
      mhd.gad_cop = "dichotomous",
      #any_mdd_diagnosis = "dichotomous",
      #any_gad_diagnosis = "dichotomous",
      mhd.social_anxiety_cop = "dichotomous",
      mhd.specific_phobia_cop = "dichotomous",
      mhd.agoraphobia_cop = "dichotomous",
      mhd.panic_disorder_cop = "dichotomous",
      mhd.panic_attacks_cop = "dichotomous",
      mhd.bipolar_disorder_cop = "dichotomous",
      mhd.ocd_cop = "dichotomous",
      mhd.bdd_cop = "dichotomous",
      mhd.an_cop = "dichotomous", 
      mhd.atypical_an_cop = "dichotomous",
      mhd.bn_cop = "dichotomous",
      mhd.bed_cop = "dichotomous",
      mhd.schizophrenia_cop = "dichotomous",
      mhd.ptsd_cop = "dichotomous",
      mhd.addadhd_cop = "dichotomous",
      phq.Q9_suicidality_binary_cop = "dichotomous"
      ),
    value = list(
      #cidid.mdd_diagnosis = "MDD diagnosis",
      #cidia.diagnosis = "GAD diagnosis",
      mhd.mdd_cop = "MDD",
      mhd.gad_cop = "GAD",
      #any_mdd_diagnosis = "MDD",
      #any_gad_diagnosis = "GAD",
      mhd.social_anxiety_cop = "Social anxiety",
      mhd.specific_phobia_cop = "Specific phobia",
      mhd.agoraphobia_cop = "Agoraphobia",
      mhd.panic_disorder_cop = "Panic disorder",
      mhd.panic_attacks_cop = "Panic attacks",
      mhd.bipolar_disorder_cop ="Bipolar disorder",
      mhd.ocd_cop = "OCD",
      mhd.bdd_cop = "BDD",
      mhd.an_cop = "AN", 
      mhd.atypical_an_cop = "Atypical AN",
      mhd.bn_cop = "BN",
      mhd.bed_cop = "BED",
      mhd.schizophrenia_cop = "Schizophrenia",
      mhd.ptsd_cop = "PTSD",
      mhd.addadhd_cop = "ADD/ADHD",
      phq.Q9_suicidality_binary_cop = "Any suicidality"
      ),
    #missing_text = "Not answered",
    digits = list(
      all_categorical() ~ c(0, 1),
      all_dichotomous() ~ c(0, 1)),
    
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})",  "{min} - {max}")
      )
    ) %>%
  add_p() %>%
  add_overall()
  

summary_table_clinical_gender
```

## Descriptive tabeles for gender glad + coping_nbr

```{r combine dat_demographics_clinical_gender and dat_demographics_clinical_gender_glad}
dat_gender_demographics <-
  dat_gender_demographics %>%
  rename_with(~ gsub("_cop$", "", .x))

dat_gender_demographics <-
  dat_gender_demographics %>%
  rename(dem.highest_education_collapsed = employ.highest_education_collapsed)

dat_gender_demographics_glad <-
  dat_gender_demographics_glad %>%
  select(-age, -height_m, -bmi)

dat_gender_glad_coping_nbr <-
  bind_rows(
    dat_gender_demographics,
    dat_gender_demographics_glad
  )
```

```{r summary_table_clinical_gender}
summary_table_clinical_gender_glad_coping_nbr <-
  dat_gender_glad_coping_nbr %>%
  gtsummary::tbl_summary(
    by = gender, 
    missing = "no",
    label = list(
      sex = "Biological sex",
      sexual_orientation = "Sexual orientation",
      ethnicity = "Ethnicity",
      employ.highest_education_collapsed_cop = "Highest education",
      mhd.mdd = "Major depressive disorder",
      mhd.gad = "Generalised anxiety disorder",
      #any_mdd_diagnosis = "Major depressive disorder",
      #any_gad_diagnosis = "Generalised anxiety disorder",
      mhd.social_anxiety = "Social Anxiety",
      mhd.specific_phobia = "Specific phobia",
      mhd.agoraphobia = "Agoraphobia",
      mhd.panic_disorder = "Panic disorder",
      mhd.panic_attacks = "Panic attacks",
      mhd.bipolar_disorder ="Bipolar disorder",
      mhd.ocd = "Obsessive-compulsive disorder",
      mhd.bdd = "Body dysmorphic disorder",
      mhd.an = "Anorexia nervosa", 
      mhd.atypical_an = "Atypical anorexia nervosa",
      mhd.bn = "Bulimia nervosa",
      mhd.bed = "Binge-eating disorder",
      mhd.schizophrenia_cop = "Schizophrenia",
      mhd.ptsd_cop = "PTSD",
      mhd.addadhd_cop = "ADD or ADHD",
      phq.Q9_suicidality_binary = "Suicidality"
),
    type = list(
      sex = "categorical",
      gender = "categorical",
      sexual_orientation = "categorical",
      
      employ.highest_education_collapsed_cop = "categorical",
      mhd.mdd = "dichotomous",
      mhd.gad = "dichotomous",
      mhd.social_anxiety = "dichotomous",
      mhd.specific_phobia = "dichotomous",
      mhd.agoraphobia = "dichotomous",
      mhd.panic_disorder = "dichotomous",
      mhd.panic_attacks = "dichotomous",
      mhd.bipolar_disorder = "dichotomous",
      mhd.ocd = "dichotomous",
      mhd.bdd = "dichotomous",
      mhd.an = "dichotomous", 
      mhd.atypical_an = "dichotomous",
      mhd.bn = "dichotomous",
      mhd.bed = "dichotomous",
      mhd.schizophrenia = "dichotomous",
      mhd.ptsd = "dichotomous",
      mhd.addadhd = "dichotomous",
      
      phq.Q9_suicidality_binary = "dichotomous"
      ),
    value = list(
      #cidid.mdd_diagnosis = "MDD diagnosis",
      #cidia.diagnosis = "GAD diagnosis",
      mhd.mdd = "MDD",
      mhd.gad = "GAD",
      #any_mdd_diagnosis = "MDD",
      #any_gad_diagnosis = "GAD",
      mhd.social_anxiety = "Social anxiety",
      mhd.specific_phobia = "Specific phobia",
      mhd.agoraphobia = "Agoraphobia",
      mhd.panic_disorder = "Panic disorder",
      mhd.panic_attacks = "Panic attacks",
      mhd.bipolar_disorder ="Bipolar disorder",
      mhd.ocd = "OCD",
      mhd.bdd = "BDD",
      mhd.an = "AN", 
      mhd.atypical_an = "Atypical AN",
      mhd.bn = "BN",
      mhd.bed = "BED",
      mhd.schizophrenia = "Schizophrenia",
      mhd.ptsd = "PTSD",
      mhd.addadhd = "ADD/ADHD",
      phq.Q9_suicidality_binary = "Any suicidality"
      ),
    #missing_text = "Not answered",
    digits = list(
      all_categorical() ~ c(0, 1),
      all_dichotomous() ~ c(0, 1)),
    
    statistic = list(
      all_categorical() ~ "{n} ({p}%)",
      all_continuous() ~ c("{mean} ({sd})", "{median} ({p25}, {p75})",  "{min} - {max}")
      )
    ) %>%
  add_p() %>%
  add_overall()

summary_table_clinical_gender_glad_coping_nbr
```

### Safe as word document

```{r word properties}
sect_properties_landscape <- officer::prop_section(
  page_size = page_size(
    orient = "landscape",
    width = 8.3,
    height = 11.7
  ),
  type = "continuous",
  page_margins = page_mar()
)
```

```{r summary_table_clinical_gender as word document}
summary_table_clinical_gender %>%
  as_flex_table() %>%
  flextable::save_as_docx(
    path = paste0(LGBTQ_folder, "tables/", date, "/LGBTQ_descriptives_clin_gender_coping_nbr", date, ".docx"),
    pr_section = sect_properties_landscape
  )
```